The \dealii Library, Version 9.7

### 2025-07-06 9.7/paper.tex
dealii-X ack.

\author[8]{Luca~Heltai}
\affil[8]{University of Pisa, Italy.}

@@

>>>>

\author[8]{Luca~Heltai}
\affil[8]{Department of Mathematics, University of Pisa, 
Via Buonarroti 1/c, 56127 Pisa, Italy.}

@@

M.~Kronbichler and L.~Heltai were partially supported by the European Research
Council (ERC) under the European Union's Horizon 2020 research and innovation
programme (call HORIZON-EUROHPC-JU-2023-COE-03, grant agreement No. 101172493
``dealii-X: an Exascale Framework for Digital Twins of the Human Body'').
